\chapter*{Acknowledgements}

Firstly, I would like to express my gratitude to my supervisor, Gavin Hesketh, without whom none of this would have been possible. Your unwavering encouragement and calmness in face of challenging problems, technical or otherwise, has made you a pleasure to work for -- thank you! 

The Fermilab Muon $g-2$ experiment is not only an impressive magnet and a large pile of interesting data, but a community of wonderful people which I have been honoured to be a part of. I would ideally thank every one of you, but I must offer particular thanks to Rebecca Chislett, Joe Price, and James Mott. The three of you are a genuine inspiration to me, not only because of your remarkable physics skills, but also because of your patience and generosity. Your support and guidance meant -- and continues to mean -- a great deal to me, and I sincerely doubt that this thesis would exist without it. I am also deeply grateful to Mark Lancaster, Chris Polly, Brendan Casey, Saskia Charity, Alex Keshavarzi, Sophie Middleton, and Nick Kinnaird for making me feel so welcome at Fermilab during my two years there, even after we were locked down due to COVID-19. I am also deeply indebted to every member, past and present, of the outstanding Europa $\omega_{a}$, tracker, and EDM groups, for their invaluable advice and support through the years. Special thanks also to Simon Corrodi, for your great help with the radial magnetic field measurements, as well as to Fred Gray, for giving me the opportunity to step out out of the office and into the lab to work on the fibre harps with you, and to Rene Fatemi, for lending me your expertise with simulation on more than one occasion. I would also like to express my sincere gratitude to Barry King, who sadly passed away during my postgraduate studies, for giving me my first opportunity to work on $g-2$ as an undergraduate summer student at Liverpool. 

This acknowledgements section would be woefully incomplete with thanking my close friends and fellow UCL $g-2$ students, Gleb Lukicov and Dominika Vasilkova, for many interesting discussions, for the camaraderie, and for this making this experience so much fun. Thanks also to Cathal Sweeney, for preserving my sanity during the several months we were locked down together, as well as to Aidan Kelly, Raif Bin Norisam, Simeon Bash, Will Quinn, and Jamie McGowan, for being such great friends to me throughout my time at UCL. To Vincenzo Monachello, thank you for bringing so much optimism and hilarity into office D25, especially during those turbulent final weeks while writing this thesis. 

Finally, to my family: Mum, Dad, James, Joey, Izzy, Momo, and Grandpa. Thank you all for the unconditional love and support, without which I would certainly not be where I am today, and for listening to me ramble about physics for the past decade or so. To Savanah, you are a source of endless inspiration to me; thank you for making these past few years the best of my life, and for reminding me what all this is supposed to be about.

% \clearpage